Filmchat

### 2017-06-14 paper/paper.tex
Updated paper again

\section{Combining the TextBlob Botlistener and the Omdbsearcher}
To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
\begin{figure}[]
  \centering
   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
  \caption{Sending a sentence to TextBlob Botlistener}
  \label{fig:sending-botlistener}
\end{figure}

\section{Combining the TextBlob Botlistener and the Omdbsearcher}
To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
\begin{figure}[]
  \centering
   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
  \caption{Sending a sentence to TextBlob Botlistener}
  \label{fig:sending-botlistener}
\end{figure}

\section{Combining the TextBlob Botlistener and the Omdbsearcher}
To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
\begin{figure}[]
  \centering
   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
  \caption{Sending a sentence to TextBlob Botlistener}
  \label{fig:sending-botlistener}
\end{figure}

\section{Combining the TextBlob Botlistener and the Omdbsearcher}
To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
\begin{figure}[]
  \centering
   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
  \caption{Sending a sentence to TextBlob Botlistener}
  \label{fig:sending-botlistener}
\end{figure}

>>>>

\section{Combining the TextBlob Botlistener and the Omdbsearcher}
To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
\begin{figure}[]
  \centering
   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
  \caption{Sending a sentence to TextBlob Botlistener}
  \label{fig:sending-botlistener}
\end{figure}
\newpage
\section{Combining the TextBlob Botlistener and the Omdbsearcher}
To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
\begin{figure}[]
  \centering
   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
  \caption{Sending a sentence to TextBlob Botlistener}
  \label{fig:sending-botlistener}
\end{figure}
\newpage
\section{Combining the TextBlob Botlistener and the Omdbsearcher}
To send a sentence to the TextBlob Botlistener, use Postman and format the message as seen in Fig\ref{fig:sending-botlistener}
\begin{figure}[]
  \centering
   \includegraphics[width=0.77\textwidth]{postman_sending_sentence_01.PNG}
  \caption{Sending a sentence to TextBlob Botlistener}
  \label{fig:sending-botlistener}
\end{figure}

\newpage
\section{Everything together, almost}
Here \(Fig\ref{fig:everything-together}\), almost all the components are playing together. I write a chat message in the designated Slack channel, while running both the Omdbsearcher, and the TextBlob botlistener, and the result, along with the sentiment gets posted to the channel.
The only part, not here, is the Speech Recognizer, as I was not able to make it recognize more than a word, here and there.

\begin{figure}[]
  \centering
   \includegraphics[width=0.77\textwidth]{everything_together.PNG}
  \caption{Everything together}
  \label{fig:everything-together}
\end{figure}
